\documentclass[12pt,letterpaper,oldfontcommands]{ucbthesis}
\usepackage[style=phys,sorting=none,biblabel=brackets,doi=true,isbn=true,eprint=true]{biblatex}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{physics}
\usepackage{graphicx}
\usepackage{nicefrac}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{array,booktabs,tabularx}
\usepackage[noabbrev]{cleveref}
\usepackage{mathrsfs}
\usepackage{scrextend}
\usepackage{bold-extra}

\hypersetup{
colorlinks   = true, %Colours links instead of ugly boxes
urlcolor     = blue, %Colour for external hyperlinks
linkcolor    = blue, %Colour of internal links
citecolor   = green, %Colour of citations
linktocpage = true,
bookmarksnumbered = true
}

\graphicspath{{figures/}}
\bibliography{citations.bib}

\begin{document}

\newcommand{\Li}{$^{8}$Li }
\newcommand{\N}{$^{16}$N }
\newcommand{\B}{$^{8}$B }
\newcommand{\snop}{SNO\raisebox{0.1ex}{\texttt{+}}}
\newcommand{\labppo}{LAB\raisebox{0.1ex}{\texttt{+}}PPO}

\title{Past, Present, and Future of Solar Neutrino Detection:\\SNO, {\snop}, and \textsc{Theia}}
\author{Benjamin J. Land}
\degreesemester{Spring}
\degreeyear{2019}
\degree{Doctor of Philosophy}
\chair{Professor Gabriel Orebi Gann}
\othermembers{Professor Yury Kolomensky \\
  Professor Kai Vetter}
\numberofmembers{3}
\prevdegrees{B.S. (Georgia Institute of Technology) 2012 \\
  M.A. (University of California, Berkeley) 2015}
\field{Physics}
\campus{Berkeley}
\maketitle
%To remove the linebreak on the approval page..
\title{Past, Present, and Future of Solar Neutrino Detection: SNO, {\snop}, and \textsc{Theia}}
\approvalpage
\title{Past, Present, and Future of Solar Neutrino Detection:\\SNO, {\snop}, and \textsc{Theia}}
\copyrightpage

\include{abstract}

\begin{frontmatter}

\begin{dedication}
\null\vfil
\begin{center}
\textit{``A witty saying proves nothing.''} \\
\hspace{100pt}---Voltaire
\end{center}
\vfil\null
\end{dedication}

\tableofcontents
\clearpage
\listoffigures
\clearpage
\listoftables
\clearpage
\include{acronyms}

\begin{acknowledgements}

I would first and foremost like to thank my adviser, Gabriel Orebi Gann, for keeping me focused while simultaneously providing a rich environment of projects, ideas, opportunities, and funding sources during the ordeal that is graduate school. 
I had no idea I would be writing a thesis on solar neutrinos when I first came to Berkeley, but after joining Gabriel's group and acclimating to the world of experimental neutrino physics, I can't imagine it any other way.
Through Gabriel, I was fortunate enough to get access to the SNO data and combined knowledge of the SNO collaboration, both of which were essential to this thesis.
In particular, I would like to thank Scott Oser, Mark Chen, and Gersende Prior for reviewing my SNO analysis, and Pierre-Luc Drouin and Stanly Seibert, whose theses were impeccable references for researching in the context of SNO.

Many thanks to Freija Descamps for helping this freshly-minted graduate student hit the ground running with the construction of the Cherenkov source, as well as for many interesting discussions growing from a shared passion for computing.
Joe Wallig brought an engineering perspective to the design of the Cherenkov source that proved to be the difference between a calibration source and a nice idea.
His help in orchestrating the use of LBNL fabrication facilities was essential.
Ryan Bayes, Peter Skensved, Rich Helmer, and Morgan Askins all put in a heroic effort to get this source deployed during {\snop}'s water phase, and it wouldn't have happened without their help.

In producing the first physics results of {\snop}, I was fortunate enough to work with Eric Marzec, whose independent analysis found just as many bugs in my code as mine did in his.
Javier Caravaca's efforts in modeling the CHESS detector and interpreting its results were instrumental in the work presented towards the end of this thesis.
Joe Wallig quickly brought CHESS from an idea on paper to a real device, saving this graduate student from having to pretend to be an engineer, and earning him a second mention.
Much gratitude goes to Minfang Yeh for conceiving of and, critically, producing the liquid scintillators studied by CHESS. 

Finally, I would like to thank my parents, Steve and Cecilia Land, and brother, Michael Land, for putting up with me all these years, and supporting me on the long road to becoming a physicist.

\end{acknowledgements}

\end{frontmatter}

\setsecnumdepth{subsection}
\settocdepth{subsection}
\pagestyle{headings}

\include{introduction}
\include{neutrino_lifetime}
\include{cherenkov_source}
\include{snoplus_solar}
\include{chess_wbls}
\include{conclusions}

\appendix

\include{appendix_qsigex}
\include{appendix_lifetime_observables}
\include{appendix_chsrc_bond}
\include{appendix_solar_bins}

\printbibliography

\end{document}

